---
title: "PR27_RPMIvCO2Indep"
author: "Liz Hughes"
date: "2022_12_16"
output: output:
  html_document:
    toc: yes
    toc_depth: 2
  word_document:
    toc: yes
    toc_depth: '2'
  pdf_document:
    toc: yes
    toc_depth: '2'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Plate reader assay 27: RPMI Vs CO2 independent media

Test WT KN99-alpha and Gat 201 deletion mutant 003(Madhani) in RPMI and CO2 independent media.
5 Bioreps, 3 Techreps each.
Grow 5ml culture from colony (1 colony = 1 Biorep) in YPD, 30C, 180 rpm ON.
Seed at OD 600nm = 0.2 , 200 ul per well.
Run for 3 days (400 cycles).

```{r load_packages}

library("reshape2")
library(dplyr)
library(ggplot2)
library(tidyverse)
library(markdown)
library(cowplot)
library(yaml)
library(knitr)
```



# Read in transposed data as csv file RPMI

```{r csv_file}

rawdata <- read.csv("../Input/PR27_RPMIvCO2_TRSP.csv")

```

# Change time in seconds to time in hours RPMI

```{r mutate_time}

 rawdata_hrs<-mutate(rawdata, Time = Time/86400)

```

# Tidy the data using the melt function from reshape2 RPMI

```{r reshape}

reshaped <- melt(rawdata_hrs, id=c("Time", "Temp"), 
                              variable.name="Well",
                              value.name="OD595")

summary(reshaped)
```

# Read in the Plate map data from csv file RPMI

```{r Load_platemap}

platemap <- read.csv("../Input/20221216_PR27_Setup.csv")
head(platemap, n=10)


```

# Combine the reshaped data with the plate map, pairing them by Well RPMI

```{r join}

annotated <- inner_join(reshaped, platemap, by="Well")
 
```

# How stable are ODs of blank wells, to use for normalisation? RPMI

```{r plot_blank_ODs}

ggplot(data=filter(annotated,Strain==""),
           aes(x=Time, y=OD595, color=Strain, group = Well)) + 
       geom_line() + 
       facet_grid(Media ~ .) +
       labs(x="Time (hrs)", y="Absorbance at 595 nm")
```


```{r plot_individual_blank_wells}

ggplot(data=filter(annotated,Well=="A2"), 
       aes(x=Time, y=OD595, color=Strain, group = Well)) + 
 
       geom_line() + 
     theme_bw()+
     labs(x="Time (hrs)", y="Absorbance at 595 nm")

```


These are very stable, except A1, A2 . Remove from normalisation.

## Calculate median OD for blank wells for each growth medium RPMI
Remove well H2

```{r calc_blank_medians}

blank_OD_summary <- annotated %>%
  filter(Strain=="") %>%
  filter(Well != "A1") %>%
  filter(Well != "A2") %>%
  # filter out columns 1 and 12 as well?
  group_by(Media) %>%
  summarise(OD_median=median(OD595),
            OD_mean=mean(OD595),
            OD_max=max(OD595),
            OD_min=min(OD595))
print(blank_OD_summary)
```

# Subtract blank OD to make corrected OD and Plot OD_corrected v Time (hrs) RPMI

```{r subtract_blank_OD}

normalisedOD <- annotated %>%
  left_join(blank_OD_summary, by="Media") %>%
  mutate(OD_corrected = OD595 - OD_median)

```

## Plot OD all RPMI

```{r plot_all}

ggplot(data=normalisedOD %>%
                      filter(Strain != ""), 
                      aes(x=Time, y=OD_corrected, color=Strain, group = Well)) + 
       geom_line() + 
       scale_y_continuous(limits=c(0,0.5),expand=c(0,0))+
       facet_wrap(Media ~ .)+
  
       labs(x = "Time(Hrs)",
            y = "Absorbance (595nm)") +
       theme(text = element_text(size = 20))+
       theme_bw()+
       scale_color_brewer(palette="Set1")
```


## Plot OD all stat_summary(geom -"line") remove excess lines RPMI

```{r plot_stat_summary}

ggplot(data=normalisedOD %>%
                     filter(Strain != ""), 
                      aes(x=Time, y=OD_corrected, color=Strain)) + 
       #geom_line(aes(group = Well), size = 0.2, alpha = 0.2) + 
       stat_summary(fun = "median", geom = "line", size = 1) +
       #scale_y_continuous(limits=c(0,0.5),expand=c(0,0), breaks = c(0, 0.05, 0.1)) +
  
       labs(x = "Number of Days",
            y = "Absorbance (595nm)",
            title = "Cell Culture Media") +
           facet_wrap(Media ~ .)+
       theme_bw() +
       theme(text = element_text(size = 15))+
       theme(axis.title = element_text(size = 25))+
       theme(axis.title.y=element_blank()) +
       theme(axis.ticks.length = unit(0.3, "cm"))+
       theme(title = element_text(size = 30))+
       theme(panel.grid.minor = element_blank())+
       theme(legend.title = element_text(size = 25))+
      theme(legend.background = element_rect(fill = "transparent", color=NA))+
  theme(legend.key = element_rect(fill = "transparent", color=NA))+
       theme (plot.background =  element_rect(fill = "transparent", color=NA), 
         panel.background = element_rect(fill = "transparent", color=NA),)+
      theme(panel.border = element_rect(linetype = "solid", colour = "black", size = 2))+
       scale_color_brewer(palette="Set1")
       
```


```{r save_RMPI_PR_Gat201_poster.png}

ggsave("../Results/AllSummary.png",width = 6.6,height=5)
```


## Plot OD all stat_summary(geom -"line") Highlight summary line RPMI

```{r plot_all_stat_summary}

ggplot(data=normalisedOD %>%
                     filter(Strain != ""), 
                      aes(x=Time, y=OD_corrected, color=Strain)) + 
       geom_line(aes(group = Well), size = 0.2, alpha = 0.2) + 
       stat_summary(fun = "median", geom = "line", size = 1) +
       #scale_y_continuous(limits=c(0,0.5),expand=c(0,0), breaks = c(0, 0.05, 0.1)) +
   facet_wrap(Media ~ .)+
       labs(x = "Number of Days",
            y = "Absorbance (595nm)",
            title = "Cell Culture Media") +
       theme_bw() +
       theme(text = element_text(size = 15))+
       theme(axis.title = element_text(size = 25)) +
  theme(axis.ticks.length = unit(0.3, "cm"))+
       theme(title = element_text(size = 30))+
       theme(legend.title = element_text(size = 25))+
  theme(panel.grid.minor = element_blank())+
       scale_color_brewer(palette="Set1")
```

```{r save_RMPI_PR_Gat201_paper.png}

ggsave("../Results/AllStatSummary.png",width = 6.6,height=5)
```


## Plot OD all stat_summary CO2

```{r plot_all_stat_summary_CO2}

ggplot(data=normalisedOD %>%
                     filter(Media =="CO2"), 
                      aes(x=Time, y=OD_corrected, color=Strain)) + 
       geom_line(aes(group = Well), size = 0.2, alpha = 0.2) + 
       stat_summary(fun = "median", geom = "line", size = 1) +
      # scale_y_continuous(limits=c(0,0.5),expand=c(0,0), breaks = c(0, 0.05, 0.1)) +
   facet_wrap(Biorep ~ .)+
       labs(x = "Number of Days",
            y = "Absorbance (595nm)",
            title = "CO2 Independent Media") +
       theme_bw() +
       theme(text = element_text(size = 15))+
       theme(axis.title = element_text(size = 25)) +
  theme(axis.ticks.length = unit(0.3, "cm"))+
       theme(title = element_text(size = 30))+
       theme(legend.title = element_text(size = 25))+
  theme(panel.grid.minor = element_blank())+
       scale_color_brewer(palette="Set1")
```

## Plot OD all stat_summary RPMI

```{r plot_all_stat_summary_CO2}

ggplot(data=normalisedOD %>%
                     filter(Media =="R"), 
                      aes(x=Time, y=OD_corrected, color=Strain)) + 
       geom_line(aes(group = Well), size = 0.2, alpha = 0.2) + 
       stat_summary(fun = "median", geom = "line", size = 1) +
       #scale_y_continuous(limits=c(0,0.1),expand=c(0,0), breaks = c(0, 0.05, 0.1)) +
   facet_wrap(Biorep ~ .)+
       labs(x = "Number of Days",
            y = "Absorbance (595nm)",
            title = "RPMI") +
       theme_bw() +
       theme(text = element_text(size = 15))+
       theme(axis.title = element_text(size = 25)) +
  theme(axis.ticks.length = unit(0.3, "cm"))+
       theme(title = element_text(size = 30))+
       theme(legend.title = element_text(size = 25))+
  theme(panel.grid.minor = element_blank())+
       scale_color_brewer(palette="Set1")
```